
\cvsection{Education}
\cvevent{Bachelor of Technology in Computer Science and Engineering - 71.2\%}{Chandigarh Group of Colleges}{ July 2012 -- July 2016}{}
\cvevent{Higher Secondary - 80.2\%}{Central Board of Secondary Education}{ 2011 }{}
\cvevent{Secondary - 86.6\% }{Central Board of Secondary Education}{ 2009 }{}
\let\orighref\href
\renewcommand{\hrefa}[2]{\orighref{#1}{#2\,\faExternalLink}}

\cvsection{Projects}
\cvproject{Topic Modeling \hrefa{https://github.com/k108/Natural-Language-Processing-Implementations/tree/master/Topic-Modeling}}
\begin{itemize}
\item Topic Modeling of News Articles using Latent Dirichlet Allocation and Non-Negative Matrix Factorization.
\end{itemize}
\cvproject{Car Price Prediction \hrefa{https://github.com/k108/CarPricePrediction}}
\begin{itemize}
\item Car price prediction using \href{https://archive.ics.uci.edu/ml/datasets/Automobile}{UCI Automobile Data Set}. This project consists of 4 jupyter notebooks in which Data Preprocessing, Exploratory Data Analysis, Model Development, and Model Evaluation is performed.
\end{itemize}
\cvproject{MultiClass Classification \hrefa{https://github.com/k108/MultiClassClassification}}
\begin{itemize}
\item It classifies the short description against labels/classes in the training data using Naive Bayesian Classifier, Tf-idf and Bag of Words.
\end{itemize}
\cvproject{Action Recommendation}
\begin{itemize}
\item Recommends actions(diagnostic or resolution) based on Configuration Item/Technology and ProblemType(using Alternating Least Squares Algorithm). It can also recommend resolution action based on diagnostic actions(cosine similarity).
\end{itemize}
\cvproject{Text Summarizer}
\begin{itemize}
\item Summarizes a given text(blog) in a given number of lines using Text Rank Algorithm.
\end{itemize}
\cvproject{Action Classification}
\begin{itemize}
\item 
It is used to fetch context based resolution actions based on list of diagnostic actions along with the execution status using Decision Tree Classifier.
\end{itemize}
\cvproject{Outage Prediction}
\begin{itemize}
\item 
It is used to predict if there will be an outage in next 24 hours based on last 3 months events(capacity, availability, performance, compliance, backup, diagnostic) data using Random Forest Classifier and Rolling Window Regression.
\end{itemize}
\cvproject{Incident Forecasting}
\begin{itemize}
\item It is used to get forecasted count of incidents for next 14 days based on last 90 days data, based on epoch time using Linear Regression with Stochastic Gradient Descent.
\end{itemize}
\cvproject{}